OSF management

### 2022-04-09 osf/manage-osf.Rmd
♻️ - add code for teams comps download

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
library(here)
library(tidyverse)
library(osfr)
library(speakr)
```

@@

```{r teams-download, eval=FALSE}
osf_teams <- osf_retrieve_node("n3fyd")
teams_comps <- osf_ls_nodes(osf_teams, n_max = Inf)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
knitr::opts_knit$set(root.dir = here::here())
library(here)
library(tidyverse)
library(osfr)
library(speakr)
library(glue)
```

@@

```{r teams-comps, eval=FALSE}
osf_teams <- osf_retrieve_node("n3fyd")
teams_comps <- osf_ls_nodes(osf_teams, n_max = Inf)
```

```{r teams-download, eval=FALSE}
for (team in 1:nrow(teams_comps)) {
  name <- teams_comps$name[team]
  dir.create(glue("./data/teams_analyses/{name}"), recursive = TRUE, showWarnings = FALSE)

  osf_ls_files(teams_comps[team,], type = "folder") %>%
    osf_download(
      path = glue("./data/teams_analyses/{name}"),
      recurse = TRUE, verbose = TRUE, progress = TRUE, conflicts = "skip"
    )
}
```
